### 2017-08-16 Tex_Dissertation/MSc_dissertation.tex
started

\begin{center}
        \huge{\bfseries Calculation of the Supersymmetric top quark mass at CLIC $e^{-}e^{+}$ collider.}\\
\end{center}

@@

Finally I would like to thank the CLICdp team that helped me. Especially
to Dr. Philipp Roloff, Dr. Marco Petric, Dr. Ignacio Garcia and Dr. Andre Sailer (all based at CERN).

@@

On July 2012 the discovery of the Higgs boson was announced at CERN's Large Hadron Collider (LHC)~\cite{aad2012observation}. 
This marked the begining of a new era for experimental High Energy Physics motivating the design of new 
experiments for further and deeper exploration of the Higgs boson itself but also, a huge marathon
addressing the questions/problems that arose with it.

One of these proposed experiments is Compact Linear Collider (CLIC), a high-luminosity linear $e^{-}$ $e^{+}$ collider. It is designed for a staging scenario of three main centre of mass energies at $\surd{s}$ = 380 GeV, $\surd{s}$ = 1.5 TeV
and $\surd{s}$ = 3 TeV targeting optimal physics output based on the current landscape. The main difference of CLIC with LHC is that in the latter, protons collide which are non fundamental particles as they consist of quarks and 
gluons bound alltogether. One of the disadvantages of LHC is the inability to know beforehand the initial state of the colliding particles as quarks exist in a "sea of gluons" making it impossible to know their momenta. This sets
some restrictions with resprect to the precision that it can probe various observables.

On the other hand, CLIC is designed to invastigate the interactions of elementary particles, an important advantage since initial states of the colliding particles is known. In advance, LHC suffers from energy loss due to 
Synchrotron radiation since protons are accelerated in a 27 km circular accelerator whereas CLIC, being linear does not.

The main targets of CLIC are dependent of the energy stage~\cite{clic2016updated}.
In the first it will focus on prescision standard model physics such as Higgs and Top quark measurements and in the two subsequent, among others, there will be searches
for new physics. One of the theories that aspires to give solutions to many of the problems of Standard Model is Supersymmetry (SUSY). In this theory every particle has a Supersymmetric partner that differs in the spin by $1/2$, thus 
relating bosons with fermions and fermions with bosons~\cite{bilal2001introduction}.

In the Minimal Supersymmetric Standard Model, the top squarks $\tilde{t}$ decay almost all the times into a top quark $t$
and a dark matter candidate, the neutralino $\tilde{\chi}_{1}^{0}$. In this project I will use Multivariate Analisis
to discriminate the best it can be achieved between signal and background with the goal to measure the top squark
mass at $\surd{s}$ = 3 TeV in the CLIC accelerator environment.

@@

Specifically, at $\surd s$ = 380 GeV and with an integrated luminosity of $\mathcal{L}_{int}$ = 500 fb$^{-1}$, 
prescision measurements can be made in the Higgs and the top quark sector~\cite{clic2016updated}.
At this enegy stage the Higgsstrahlung
process ($e^{+}e^{-}\rightarrow ZH$) alongside the $WW$ fusion ($e^{+}e^{-}\rightarrow H\nu_{e}\tilde{\nu}_{e}$) 
are the dominant and can shed light to properties of the Higgs boson in a model independent way.
In CLIC there is also a dedicated program for top quark physics. This is because it is one of the most important particles
in SM because it couples strongest to the Higgs field due to its mass but also it has an important role in 
many of the BSM scenarios.
Furthermore at the next two stages, leading role will play the proposed scenarios for physics BSM with most 
importantly Supersymmetry at $\surd s$ = 3 TeV and with $\mathcal{L}_{int}$ = 3000 fb$^{-1}$. This  is because CLIC has the potential for direct particle detection up to the 
kinematic limit of $\surd s /2$ for pair production. Also through indirect detection of observables that are sensitive to BSM
scenarios, precision measurements can be made, and comparison with the SM expectations can yield unexpected 
divergencies, 
taking advantage of the full energy potential.

Given the linear nature of CLIC, there are no energy losses induced by Synchrotron radiation which appears in 
circular colliders, but due Beamsstrahlung radiation. As the colliding bunches get closer to the 
vertex, the strong electromagnetic fields (up to 10 Tesla) created by the opposing beam, cause deflection
of the partices trajectories resulting to emit Synchrotron radiation. The effect is energy-dependent with huge
impact at higher energies~\cite{bonvicini1989first} as it can be seen in the following 
image~\cite{abramowicz2017higgs}.

@@

Furthermore, the experiment has two detector concepts: CLIC SiD and CLIC ILD, in order to serve the required 
jet energy resolution. The latter has been  developed for the International Linear Collinder but it has been
adapted according to the needs of CLIC. Both detectors have strong central solenoid magnets creating an axial 
magnetic field of 5T for CLIC SiD and 4T for CLI ILD~\cite{abramowicz2017higgs}.

@@

The model that describes elementary particle physics is the Standard Model~\cite{cheng1984gauge}.
It involves matter  fields (fermions)
and vector gauge bosons (force carriers) that they stem from the fact that the SM Lagrngian is subject to $SU(3) \otimes 
SU(2) \otimes U(1)$ symmetries. An important part of this theory is the existence of the Higgs field which appeared
during the unification of the electromagnetic and the weak force. It is known for the fact that it "gives"
mass to the elementary particles (besides photons and gluons which they are protected by the $U(1)$,$SU(3)$
unbreakable symmetries respectively)
via Spontaneous Symmetry Breaking .

@@

\begin{equation}
 \int_{}^{\Lambda} d^{4}k \quad f(k,external\quad momenta)
\end{equation}

where $\Lambda$ represents the scale of the new physics such as the effects of quantum gravity. In dimensional 
regularisation, when $\Lambda \rightarrow \infty$ the renormalisability of the theory assures that there
is no inconsistency; but if we take into account a scale such as the quantum gravity, then $\Lambda \rightarrow 
M_{P} \approx 1.2\times 10^{19}\quad \textrm{GeV}$ which is the Plank mass. In that case 
the additive quantum corrections for the Higgs 
mass become too big dragging the value of the Higgs mass up. Because the VEV of the Higgs boson has a fixed 
phenomenologicaly value, one way to circumvent this problem is by relating bosons with fermions. 
This constitutes a solution since in the 
latter, the algebraic terms for their self energies come with a minus sign giving the desired cancelations 
without any "fine tuning" from our side. This results into the SUSY theory stabilising the Hierarchy $M_{H}
\ll M_{P}$ with the constraint that the SUSY particles should be visible at a scale not too much greater 
than 1-10 TeV.

@@

The framework of this project is the Minimal Supersymmetric Standard Model which besides the SM particles 
includes the sleptons $\tilde{\ell}^{\pm}$, the sneutrinos $\tilde{\nu}_{l}$, the squarks $\tilde{q}$, the 
gluinos $\tilde{g}$, two pair of charginos $\tilde{\chi}^{\pm}_{i}$ where $i=1,2$ ,  four neutralinos 
$\tilde{\chi}^{0}_{i}$, $i=1,...,4$ and five Higgs bosons $\tilde{h}^{0}$, $\tilde{H}^{0}$,
$\tilde{A}^{0}$,$\tilde{H}^{\pm}$.

@@

In Standard Model, for the Spontaneous Symmetry Breaking one Higgs doublet is needed with 4 degrees of 
freedom (complex). For the SUSY model on the other hand, two such doublets are required with a total of eight 
degrees of freedom. The supersymmertric partners of the SM Higgs, the Higgsinos, mix with the Winos 
$\tilde{W}^{\pm}$ and the 
Binos $\tilde{B}$ in order to form the neutralinos $\tilde{\chi}_{i}^{0}$ and the charginos 
$\tilde{\chi}_{i}^{\pm}$.

@@

It is known that within the SM the fermions carry chirality denoted by L or R whether they are left or right 
respectively, according to the way they transform under the symmetry group $SL(2,\mathbb{C})$. Thus given 
the SUSY relation of fermions-bosons that means that the sfermions  (bosonic superpartners), come into 
doublets of the form $(f_{i},\tilde{f}_{i})$, where i=L,R. The sfermions mix further to make the eigenstates
of the mass matrix. This mixing is expected to be strong for third generation sfermions since the Yukawa 
couplings can be large. More precisely in our case the stop quark mixing effects can be large because
of the large mass of the top quark.

@@

In this project I will focous on the top squarks  where the mixing   $\tilde{t}_{R}-\tilde{t}_{L}$ is important
due to the large top quark mass. By computing the eigenvalues of the previous matrix and for the right
flavour, we obtain:

@@

It is obvious that the $m^{2}_{\tilde{t}_{1}}$ will have the lowest mass, something that makes it the 
lightest squark.

@@

 The search for indications for Supersymmetry is not new as LHC has been optimized and focused among other
 to the direct or indirect detection of sparticles~\cite{chatrchyan2011search}.
The majority of the cases that have been studied, consider as main decay channel of the sparticles 
the following:

@@

So far thought no indication of SUSY has been found in LHC but through each analysis the exclusion limits 
for the SUSY observables become bigger and bigger as it can be seen in the figure 3.1 that summarises
the latest of them for the stop quark mass at $\surd s$ = 8/13 GeV in proton proton collisions
~\cite{aaboud2016search}.

\begin{figure}[!hb]
  \centering
  \includegraphics[width=0.7\linewidth]{{images/ATLAS_SUSY_Stop_tLSP}.png}
  \label{fig2.15}
  \caption{\scriptsize{Mass exclusion limits at stop-neutralino plane (combined summary plot from ATLAS 
  twiki).}}
\end{figure}

Whereas in the figure 3.2 there are the latest exclusion limits in ATLAS for p-p collisions at 13 TeV in the gluino-
stop plane.

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.6\linewidth, scale=5]{{images/gluino}.png}
  \label{}
  \caption{\scriptsize{Mass exclusion limits at stop-gluino plane~\cite{atlassearch}.}}
\end{figure}

@@

In this chapter I will describe the exact conditions and methods that were followed in this project for the 
calculation of the stop quark mass at CLIC Conceptual experiment.

I will invedtigate the production of a pair of stop quarks at $\surd s$ = 3 TeV and assumig an  integrated 
luminosity of $\mathcal{L}_{int}$ = 3000 fb$^{-1}$. The channel of interest is the following:

@@

and for this model the mass of the top squark is $m_{\tilde{t}}$ = 845 GeV whereas the mass of the 
neutralino is $m_{\tilde{\chi}_{1}^{0}}$= 357 GeV. This is not the only possible decay of a top squark but it is the
dominant one. In what follows I show the top three branching ratios of the top squark decay and two
of the corresponding Feynmann diagrams:

@@

As also the branching ratios for the decay of the W boson to either in a hadronic final state or in
a leptonic one are:

@@

\begin{itemize}
 \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t \tilde{\chi}_{1}^{0}
 \chi^{\pm}_{1}b \rightarrow
 W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}$ \quad (35.8\%)

@@

 \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t\bar{t} \tilde{\chi}_{1}^{0}
 \chi^{0}_{2} \rightarrow
 W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}h$ \quad (13.7\%)

 \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow b\bar{b} \chi_{1}^{+}
 \chi^{-}_{1} \rightarrow
 W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}$ \quad (11.6\%)

 \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t \tilde{\chi}_{2}^{0}
 \chi^{\pm}_{1}b \rightarrow
 W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}h$ \quad (9\%)

@@

\section{Calculation of SUSY particle masses}

@@

The main topologies that are considered are those that the gluino is heavier than the squarks and thus the 
dominant decaying channel is:

@@

This technique has been developed initially for LHC experiment where the p-p collision energy is not known.
The calculation was achieved by creating the variable $M_{C}$ which is related to the standard 
invariant mass but it's invariance comes from contra linear boosts of equal magnitude. The squark mass is given
by:

@@

\begin{equation}
 M_{C}^{2}=2(E_{q,1}E_{q,2}+\vec{p}_{q,1}\vec{p}_{q,2})
\end{equation}

@@

The power off this kind of calculation comes from the fact that no knowledge for the exact center of mass 
energy is needed (In comparison with the first method described in~\cite{simon2010techniques}), something that is not purely known since the effects of initial state radiation and
the Beamstrahlung can distort it significantly resulting to even bigger uncertainties. Note that this method 
assumes that the mass of the neutralino is known and that the quark is massless.

@@

In this chapter I describe the procedure that I followed until the calculation of the top squark mass. 
This involved the vertex finding, the jet clustering, the flavourtagging and the calculation of the $\chi^{2}$
for each template of the top squark mass.

@@

>>>>

\begin{center}
        \huge{\bfseries Measurement of the Supersymmetric top quark mass at CLIC $e^{-}e^{+}$ collider.}\\
\end{center}

@@

Finally I would like to thank the CLICdp team that helped me. Especially
Dr. Philipp Roloff, Dr. Marco Petric, Dr. Ignacio Garcia and Dr. Andre Sailer (all based at CERN).

@@

On July 2012 the discovery of the Higgs boson was announced at CERN's Large Hadron Collider (LHC)~\cite{aad2012observation}
~\cite{higgs1966spontaneous}. 
This marked the begining of a new era for experimental High Energy Physics motivating the design of new 
experiments for further and deeper exploration of the Higgs boson itself but also, a huge marathon
addressing the questions/problems that arose with it.

One of these proposed experiments is Compact Linear Collider (CLIC), a high-luminosity linear $e^{-}$ $e^{+}$ collider. It is designed for a staging scenario of three main centre of mass energies at $\surd{s}$ = 380 GeV, $\surd{s}$ = 1.5 TeV
and $\surd{s}$ = 3 TeV targeting optimal physics output based on the current landscape~\cite{clic2016updated}. 
The main difference of CLIC with LHC is that in the latter, protons collide which are non fundamental particles as they consist of quarks and 
gluons bound alltogether. One of the disadvantages of LHC is the inability to know beforehand the initial state of the colliding particles as quarks exist in a "sea of gluons" making it impossible to know their momenta. This sets
some restrictions with resprect to the precision that it can probe various observables.

On the other hand, CLIC is designed to invastigate the interactions of elementary particles, an important advantage since initial states of the colliding particles is known. In addition, LHC suffers from energy loss due to 
Synchrotron radiation since protons are accelerated in a 27 km circular accelerator whereas CLIC, being linear does not.

The main targets of CLIC are dependent of the energy stage~\cite{clic2016updated}.
In the first it will focus on prescision standard model physics such as Higgs and top quark measurements and in the two subsequent, among others, there will be searches
for new physics. One of the theories that aspires to give solutions to many of the problems of Standard Model is Supersymmetry (SUSY). In this theory every particle has a Supersymmetric partner that differs in the spin by $1/2$, thus 
relating bosons with fermions and fermions with bosons~\cite{bilal2001introduction}.

In the Minimal Supersymmetric Standard Model, the top squarks $\tilde{t}$ can decay into a top quark $t$
and a dark matter candidate, the neutralino $\tilde{\chi}_{1}^{0}$. In this project I will use multivariate analysis
to discriminat between signal and background with the goal to measure the top squark
mass at $\surd{s}$ = 3 TeV in the CLIC accelerator environment.

@@

Specifically, at $\surd s$ = 380 GeV and with an integrated luminosity of $\mathcal{L}_{int}$ = 500 fb$^{-1}$, 
prescision measurements can be made in the Higgs and the top quark sector~\cite{clic2016updated}.
At this enegy stage the Higgsstrahlung
process ($e^{+}e^{-}\rightarrow ZH$) alongside the $WW$ fusion ($e^{+}e^{-}\rightarrow H\nu_{e}\tilde{\nu}_{e}$) 
are the dominant and can shed light to properties of the Higgs boson in a model independent way.
In CLIC there is also a dedicated program for top quark physics. This is because it is one of the most important particles
in SM because it couples strongest to the Higgs field due to its mass but also it has an important role in 
many of the BSM scenarios.
Furthermore at the next two energy stages, investigations will be done with respect to 
proposed scenarios for physics BSM with most 
importantly Supersymmetry at $\surd s$ = 3 TeV and with $\mathcal{L}_{int}$ = 3000 fb$^{-1}$. This  is because CLIC has the potential for direct particle detection up to the 
kinematic limit of $\surd s /2$ for pair production. Also through indirect detection of observables that are sensitive to BSM
scenarios, precision measurements can be made, and comparison with the SM expectations can yield unexpected 
divergencies, 
taking advantage of the full energy potential.

Given the linear nature of CLIC, there are no energy losses induced by Synchrotron radiation which appears in 
circular colliders, but due Beamsstrahlung radiation. As the colliding bunches get closer to the 
vertex, the strong electromagnetic fields (up to 10 Tesla) created by the opposing beam, cause deflection
of the partices trajectories resulting to emit Synchrotron radiation. The effect is energy-dependent with huge
impact at higher energies~\cite{bonvicini1989first} as it can be seen in figure 
2.1~\cite{abramowicz2017higgs}.

@@

Furthermore, the experiment has two detector concepts: CLIC SiD and CLIC ILD. 
Both have been  developed for the International Linear Collinder but it has been
adapted according to the needs of CLIC. Both detectors have strong central solenoid magnets creating an axial 
magnetic field of 5T for CLIC SiD and 4T for CLI ILD~\cite{abramowicz2017higgs}.

@@

The model that describes elementary particle physics is the Standard Model~\cite{cheng1984gauge}~\cite{weinberg1967model}.
It involves matter fields (fermions)
and vector gauge bosons (force carriers) that they stem from the fact that the SM Lagrangian is subject to $SU(3) \otimes 
SU(2) \otimes U(1)$ symmetries. An important part of this theory is the existence of the Higgs field which appeared
during the unification of the electromagnetic and the weak force. It is known for the fact that it "gives"
mass to the elementary particles (besides photons and gluons which they are protected by the $U(1)$, $SU(3)$
unbreakable symmetries respectively)
via Spontaneous Symmetry Breaking.

@@

\begin{equation}
 \int_{}^{\Lambda} d^{4}k \quad f(k,\textrm{external momenta})
\end{equation}

where $\Lambda$ represents the scale of the new physics such as the effects of quantum gravity. In dimensional 
regularisation, when $\Lambda \rightarrow \infty$ the renormalisability of the theory assures that there
is no inconsistency; but if we take into account a scale such as the quantum gravity, then $\Lambda \rightarrow 
M_{P} \approx 1.2\times 10^{19} \textrm{GeV}$ which is the Plank mass. In that case 
the additive quantum corrections for the Higgs 
mass become too big dragging the value of the Higgs mass up. Because the VEV of the Higgs boson has a fixed 
phenomenologicaly value, one way to circumvent this problem is by relating bosons with fermions. 
This constitutes a solution since in the 
latter, the algebraic terms for their self energies come with a minus sign giving the desired cancelations 
without any "fine tuning" from our side. This results into the SUSY theory stabilising the Hierarchy $M_{H}
\ll M_{P}$ with the constraint that the SUSY particles should be visible at a scale not too much greater 
than 1-10 TeV.

@@

The framework of this project is the Minimal Supersymmetric Standard Model.

@@

The MSSM includes the sleptons $\tilde{\ell}^{\pm}$, the sneutrinos $\tilde{\nu}_{l}$, the squarks $\tilde{q}$, the 
gluinos $\tilde{g}$, two pair of charginos $\tilde{\chi}^{\pm}_{i}$ where $i=1,2$ ,  four neutralinos 
$\tilde{\chi}^{0}_{i}$, $i=1,...,4$ and five Higgsinos $\tilde{h}^{0}$, $\tilde{H}^{0}$,
$\tilde{A}^{0}$,$\tilde{H}^{\pm}$.
In Standard Model, for the Spontaneous Symmetry Breaking one Higgs doublet is needed with 4 degrees of 
freedom (complex). For the SUSY model on the other hand, two such doublets are required with a total of eight 
degrees of freedom. The supersymmertric partners of the SM Higgs, the Higgsinos, mix with the Winos 
$\tilde{W}^{\pm}$ and the 
Binos $\tilde{B}$ in order to form the neutralinos $\tilde{\chi}_{i}^{0}$ and the charginos 
$\tilde{\chi}_{i}^{\pm}$.

@@

It is known that within the SM the fermions carry chirality denoted by L or R whether they are left or right 
respectively, according to the way they transform under the symmetry group $SL(2,\mathbb{C})$. Thus given 
the SUSY relation of fermions-bosons that means that the sfermions  (bosonic superpartners), come into 
doublets of the form (SM particle, SUSY partner), i.e.: $(f_{i},\tilde{f}_{i})$, where i=L,R. 
The sfermions mix further to make the eigenstates
of the mass matrix. This mixing is expected to be strong for third generation sfermions since the Yukawa 
couplings can be large. More precisely in our case the top squark mixing effects can be large because
of the large mass of the top quark.

@@

In this project I will focus on the top squarks  where the mixing   $\tilde{t}_{R}-\tilde{t}_{L}$ is important
due to the large top quark mass. By computing the eigenvalues of the previous matrix and for the right
flavour, we obtain:

@@

It is obvious that the $m^{2}_{\tilde{t}_{1}}$ will have the lowest mass, something that makes it
probably the lightest squark.

@@

 The search for indications for Supersymmetry is not new as LHC has been optimized and focused among other
 to the direct or indirect detection of sparticles~\cite{chatrchyan2011search}.
The majority of the cases that have been studied, consider as main decay channel of the squarks 
the following:

@@

So far thought no indication of SUSY has been found in LHC but through each analysis the exclusion limits 
for the SUSY observables become bigger and bigger. This can be seen in the figure 3.1 
that summarises
the latest exclusion limits for the top squark mass at $\surd s$ = 8/13 GeV in proton proton collisions
~\cite{aaboud2016search}.
Whereas in the figure 3.2 are the latest exclusion limits in ATLAS for p-p collisions at 13 TeV in the gluino -
stop plane.

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.6\linewidth]{{images/ATLAS_SUSY_Stop_tLSP}.png}
  \label{fig2.15}
  \caption{\scriptsize{Mass exclusion limits at stop-neutralino plane (combined summary plot from ATLAS 
  twiki).}}
\end{figure}

%Whereas in the figure 3.2 there are the latest exclusion limits in ATLAS for p-p collisions at 13 TeV in the gluino-
%stop plane.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.6\linewidth, scale=5]{{images/gluino}.png}
  \label{}
  \caption{\scriptsize{Mass exclusion limits at stop-gluino plane~\cite{atlassearch}.}}
\end{figure}

@@

In this chapter I will describe the exact conditions and methods that were followed in this project for the 
measurement of the stop quark mass at the CLIC Conceptual experiment.

I investigate the production of a pair of top squarks at $\surd s$ = 3 TeV and assuming an  integrated 
luminosity of $\mathcal{L}_{int}$ = 3000 fb$^{-1}$. The channel of interest is the following:

@@

and for this model the mass of the top squark is $m_{\tilde{t}}$ = 845 GeV (denoted as $M_{nom}$ later
in the text)
whereas the mass of the 
lightest neutralino is $m_{\tilde{\chi}_{1}^{0}}$= 357 GeV. This is not the only possible decay of a top 
squark but it is the
dominant one. In what follows I show the top three branching ratios of the top squark decay and two
of the corresponding Feynmann diagrams:

@@

Also, the branching ratios for the decay of the W boson to either a hadronic final state or 
a leptonic one are:

@@

\begin{itemize}
 \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t \tilde{\chi}_{1}^{0}
 \tilde{\chi}^{\pm}_{1}b \rightarrow
 W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}$ \quad (35.8\%)

@@

 \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t\bar{t} \tilde{\chi}_{1}^{0}
 \tilde{\chi}^{0}_{2} \rightarrow
 W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}h$ \quad (13.7\%)

 \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow b\bar{b} \tilde{\chi}_{1}^{+}
 \tilde{\chi}^{-}_{1} \rightarrow
 W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}$ \quad (11.6\%)

 \item $e^{-}e^{+} \rightarrow \tilde{t}\tilde{\bar{t}} \rightarrow t \tilde{\chi}_{2}^{0}
 \tilde{\chi}^{\pm}_{1}b \rightarrow
 W^{+}W^{-} b \bar{b} \tilde{\chi}_{1}^{0}  \tilde{\chi}_{1}^{0}h$ \quad (9\%)

@@

\section{Measurement of SUSY particle masses}

@@

The main topologies that are considered are those that the gluino is heavier than the squarks and thus the 
dominant production and decay channel is:

@@

This technique has been developed initially for LHC experiment where the energy that is used
to make the squark - antisquark pair is not known.
The calculation was achieved by creating the variable $M_{C}$ which is related to the standard 
invariant mass but it's invariance comes from contra linear boosts of equal magnitude. The squark mass is given
by:

@@

\begin{equation}
 M_{C}^{2}=2(E_{q,1}E_{q,2}+\vec{p}_{q,1}\cdot \vec{p}_{q,2})
\end{equation}

@@

The power off this kind of calculation comes from the fact that no knowledge for the exact center of mass 
energy is needed (In comparison with the first method described in~\cite{simon2010techniques}), something that is not purely known since the effects of initial state radiation and
the Beamstrahlung can distort it significantly resulting to even bigger uncertainties. Note that this method 
assumes that the mass of the neutralino is known and that the quark is massless and therefore
unsuitable for the mass measurement of the top squark.

@@

In this chapter I describe the procedure that I followed until the calculation of the top squark mass. 
This involved vertex finding, jet clustering, flavour tagging and the calculation of the $\chi^{2}$
for each template of the top squark mass.

@@

The point that particles collide in a collider experiment is called primary vertex or interaction 
point (IP). After that 
collision, it is possible that some of the particles will decay further away from the IP. The point 
that this decay takes place is called secondary vertex. Every analysis that involves jet clustering
procedure (and not only) has as starting point the vertex finding. This involves an algorithm
